\definecolor{garnetred}{rgb}{0.6, 0, 0}
\colorlet{COGcolor}{garnetred}   %new color names can be defined before use
\journalcolor      {COGcolor} %a color name.
\journaltitle      {Foundations and Trends\textsuperscript{\textregistered} in Cognitive Science}
\journaltitleprefix{Foundations and Trends\textsuperscript{\textregistered} in}
\journalshorttitle {COG}
\journalurl        {http://www.nowpublishers.com/COG}
\journalissnprint  {} % TBD
\journalissnonline {} % TBD
\journaldoi        {10.1561/xx} % TBD

\journalcopyrightowner{now Publishers Inc.}

\journalbibstyle{author} % either author or numeric

\journalaimsandscope
 {%
\subsection*{Aims}
The growth in all aspects of research in the last decade has led to a multitude of new publications 
and an exponential increase in published research. Finding a way through the excellent existing literature 
and keeping up to date has become a major time-consuming problem. Electronic publishing has given researchers 
instant access to more articles than ever before. But which articles are the essential ones that should 
be read to understand and keep abreast with developments of any topic? To address this problem Foundations 
and Trends\textsuperscript{\textregistered} in Cognitive Science publishes high-quality survey and tutorial monographs of the field.

Each issue of Foundations and Trends\textsuperscript{\textregistered} in Cognitive Science comprises a 50-100 page 
monograph written by research leaders in the field. Monographs that give tutorial coverage of subjects, 
research retrospectives as well as survey papers that offer state-of-the-art reviews fall within the scope 
of the journal.
 \subsection*{Scope}
Foundations and Trends\textsuperscript{\textregistered} in Cognitive Science publishes surveys and tutorials on the foundations of human-computer interaction. The scope is broad. The list of topics below is meant to illustrate some of the coverage, and is not intended to be an exhaustive list.
}


\journallibraryinfo
 {%
  Foundations and Trends\textsuperscript{\textregistered} in
  Cognitive Science, \useissuedata{pubyear},
  Volume~\useissuedata{volume}, 4 issues.
  ISSN paper version \usejournaldata{issnprint}.
  ISSN online version \usejournaldata{issnonline}.
  Also available as a combined paper and online
  subscription.
 } 