\definecolor{darkorange}{rgb}{0.89, 0.32, 0.02} % TBD
\colorlet{STAcolor}{darkorange}   %new color names can be defined before use  % TBD
\journalcolor      {STAcolor} %a color name.
\journaltitle      {Foundations and Trends\textsuperscript{\textregistered} in Statistics}
\journaltitleprefix{Foundations and Trends\textsuperscript{\textregistered} in}
\journalshorttitle {STA}
\journalurl        {http://www.nowpublishers.com/STA}
\journalissnprint  {} % TBD
\journalissnonline {} % TBD
\journaldoi        {10.1561/} % TBD

\journalcopyrightowner{now Publishers Inc.}

\journalbibstyle{author} % either author or numeric

\journalaimsandscope
 {%
 \subsection*{Aims}
The growth in all aspects of research has led to a multitude of new publications and an exponential increase in published research. Finding a way through the excellent existing literature and keeping up to date has become a time-consuming problem. Researchers have instant access to more articles than ever before. But which articles are the essential ones that should be read to understand and keep abreast with developments of any topic? To address this problem Foundations and Trends\textsuperscript{\textregistered} in Statistics publishes high-quality short monographs that provide a starting point for a graduate student or researcher new to a particular topic.
 
Each issue of Foundations and Trends\textsuperscript{\textregistered} in Statistics comprises a monograph of at least 50 pages written by research leaders in the field. We aim to publish monographs that provide an in-depth, self-contained treatment of topics where there have been significant new developments. Typically, this means that the monographs we publish will contain a significant level of mathematical detail (to describe the central methods and/or theory for the topic at hand), and will not eschew these details by simply pointing to existing references. Literature surveys and original research papers do not fall within these aims.
 \subsection*{Scope}
Foundations and Trends\textsuperscript{\textregistered} in Statistics publishes research monographs on fundamental problems in statistics and its applications. We are interested in monographs that focus on statistical theory, methodology, and/or applications, as well as intersections of statistics with related fields including (but not limited to) optimization, machine learning, and probability.
 }


\journallibraryinfo
 {%
  Foundations and Trends\textsuperscript{\textregistered} in
  Statistics, \useissuedata{pubyear},
  Volume~\useissuedata{volume}, 4 issues.
  ISSN paper version \usejournaldata{issnprint}.
  ISSN online version \usejournaldata{issnonline}.
  Also available as a combined paper and online
  subscription.
 } 